Dirac integration with a general purpose bookkeeping DB: a complete general suite for distributed resources exploitation

### 2013-10-01 CHEP2013/paper/paper.tex
test description

\author{M Chrząszcz, C De Santis, G Donvito, A Fella, R Grzymkowski, B Santeramo, L Tommassetti, M Zdybał}
%\address{\textsuperscript {1} Institution, Country}
\ead{bruno.santeramo@ba.infn.it}

@@

@@

@@

\section{Test session}
% Bruno
A test session was performed aiming to demonstrate the awareness of SuperBDIRAC to integrate the monitoring of a bookkeeping database in DIRAC.
\subsection{Goal description}
DIRAC capabilities and performance as job management tool are well documented (insert some reference). Super$B$ distributed simulation stack (WebUI + SBK + Severus) was successfully used in 3 simulation campaigns (ask to Armando for confirmation and references).\\
Test goal was to demonstrate SuperBDIRAC is capable of substitute WebUI as monitoring tool for job submission, showing data from a bookkeeping database. Test "Q-factor" was the exact corrispondence of information as stored in SBK and displayed in SuperBDIRAC, like in WebUI monitoring page. Correct execution of simulation jobs is not important while the bookkeping information are properly managed.

@@

FastSim job submission is created via WebUI interface (see figure to be inserted). Once submission is created, a set of scripts and configuration files are created whose path is reported by WebUI interface: in particular the path of php submission script is taken to be be parsed. Since WebUI is still linked with SBK, this portal acts as well as monitoring portal, useful for a check-cross between info displayed in SBK, WebUI and SuperBDIRAC.\\

A python script (mc\_production.py) acts as parser for php submission script and interface with DIRAC client. Once taken all submission parameter, mc\_production.py uses DIRAC API to submit jobs to DIRAC server.\\

@@

In SBK the job submission insertion is performed by WebUI, while later info are updated by Severus script executed with every job submitted. Severus interact with SBK via REST interface, while WebUI and SuperBDIRAC have direct acces to SBK since they are in the same LAN area (ask to Armando for confirmation).\\

@@

Every job simulated 3000 events: this value was chosen to have an execution time of about 10 minutes.
Physical parameters were the same of several official productions.
3 main bunch submission of 400 jobs were performed at INFN-T1 to obtain a total 1200 simulations.
In addition, 2 bunch submission of 10 jobs were performed, again at INFN-T1, to force some failure message in SBK and catch it even in SuperBDIRAC monitoring. In summary, 1220 jobs were submitted for test.\\

Since test goal, several screenshots of WbUI and SuperBDIRAC monitoring were saved, in addition to SBK data screenshots.

@@

@@

- We are offering a Dirac extended suite capable to satisfy the
needs onsmall and mid size VOs in terms of distributed
resource exploitation....

@@

>>>>

\author{M Chrzaszcz, C De Santis, G Donvito, A Fella, R Grzymkowski, B Santeramo, L Tommassetti, M Zdybal}
%\address{\textsuperscript {1} Institution, Country}
\ead{bruno.santeramo@ba.infn.it}

@@

\begin{figure}[h]
\includegraphics[width=26pc]{img/distributed_system_bird_eye.eps}\hspace{2pc}%
\caption{\label{fig:distributed_system_bird_eye_view}Distributed System bird's eye view.}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=26pc]{img/BK_entities.eps}\hspace{2pc}%
\caption{\label{fig:BK_entities}Entities in BookKeeping database.}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=26pc]{img/simulation_production_system_workflow.eps}\hspace{2pc}%
\caption{\label{fig:simulation_production_workflow}Simulation Production workflow.}
\end{figure}

\begin{figure}[h]
\includegraphics[width=26pc]{img/SuperBDIRAC_monitoring.eps}\hspace{2pc}%
\caption{\label{fig:superbdirac_monitoring}Monitoring job data from SBK in DIRAC.}
\end{figure}

\section{Functionality Test}
% Bruno
A functionality test was performed to demonstrate the capability of SuperBDIRAC to integrate the monitoring of a bookkeeping database in DIRAC webportal.
\subsection{Goal description}
DIRAC capabilities and performance as job management tool are well documented (insert some reference). Super$B$ distributed simulation stack (WebUI + SBK + Severus) was successfully used in 3 simulation campaigns (ask to Armando for confirmation and references).\\
Functionality Test goal is to demonstrate if SuperBDIRAC is capable of substitute WebUI as monitoring tool for job submission, showing data from a bookkeeping database. Test "Q-factor" is the exact correspondence of information as stored in SBK and displayed in SuperBDIRAC, like in WebUI monitoring page. Correct execution of simulation jobs is not important while the bookkeping information are properly managed.

@@

At present time, not all WebUI functionalities are implemented in SUperBDIRAC, in particular "Submission" job for a given "Request".
The following procedure was followed to perform this test. FastSim job submission is created via WebUI interface. Once submission is created, a set of scripts and configuration files are created whose path is reported by WebUI interface: in particular the path of php submission script is taken to be be parsed. This php submission script, generated by WebUI, is made of an array with all relevant parameters and commands to UI in order to submit jobs in grid via standard glite commands.
Since WebUI is still linked with SBK, this portal could be used as well as monitoring portal, useful for a check-cross between info displayed in SBK, WebUI and SuperBDIRAC.\\

The php submission script is parsed by a python script (mc\_production.py), in particular the params array, in order to retrieve all needed paramenters to properly submit jobs: production series, session name, min and max runnumber, configuration files location, physical parameters, events to simulate. Once taken all these parameters, mc\_production.py uses DIRAC API to prepare and submit jobs via DIRAC client.

@@

In SBK the job submission insertion is performed by WebUI, while later info are updated by Severus script executed with every job submitted. Severus interact with SBK via REST interface, while WebUI and SuperBDIRAC have direct access to SBK since they are in the same LAN area (ask to Armando for confirmation).\\

@@

Every job simulated 3000 events: this value is set to have an execution time quite longer than 10 minutes.
Physical parameters are the same of other official productions.
3 main bunch submission of 400 jobs were performed at INFN-T1 to obtain a total of 1200 simulations.
Status in SBK were "prepared", "running" and "done".
In addition, 2 bunch submission of 10 jobs were performed, again at INFN-T1, to force some failure message in SBK and catch it even in SuperBDIRAC monitoring. First failure sample was obtained setting a not-existing site as destination for stageout: error was detected during preliminary check, so status in SBK were "prepared" and "failed". In second failure sample, jobs were submitted using a proxy without Role=ProductionManager, so error occurred in stageout phase: status in SBK were "prepared", "running" and "failed". In summary, 1220 jobs were submitted for test.\\

Since test goal, several screenshots of WebUI and SuperBDIRAC monitoring were saved, in addition to SBK data screenshots.

@@

For each tests, all jobs were submitted at same time. Job execution depends on queue occupancy. Since we were interested in bookkeeping database status updates and not in measuring DIRAC performance in job execution, no dedicated CPU slots were asked for. While failing jobs were all executed simultaneously (10 dedicated CPU were always available for Super$B$ at INFN-T1), for 400 jobs tests simulation execution was spread on a greater time interval (see table \ref{tab:execution_time}).

\begin{table}[h]
\caption{
  \label{tab:execution_time}
  Execution time calculated as difference between Submission time and End Time in DIRAC scheduling system.
}
\begin{center}
\begin{tabular}{lrrr}
\br
test & mean time (sec) & min time (sec) & max time (sec)\\
\mr
good-1 & 2203,66 & 859,00 & 5048,00\\
good-2 & 1102,92 & 832,00 & 2597,00\\
good-3 & 1188,62 & 849,00 & 4716,00\\
failure-1 & 165,10 & 161,00 & 172,00\\
failure-2 & 901,50 & 874,00 & 935,00\\
\br
\end{tabular}
\end{center}
\end{table}

Mean and max time could be interesting for performance measurements, but for this functionality test min time must be considered since it's related to execution time of job ran once submitted. First 3 good test have similar min time, compatible with estimated 13 minutes for simulation. For failure test, in first case the low min time is due to forced error in preliminary check phase (jobs fail without executing simulation code), in second case jobs execute simulation code but fail trying stageout (due to wrong Role-based permission in writing INFN-T1 storage area), so min time is longer as expected.

\begin{table}[h]
\caption{\label{tab:status_update}Job status in SBK, WebUI and SuperBDIRAC.}
\begin{center}
\begin{tabular}{lrlrrrr}
\br
test & jobs & site & SBK status & WebUI status & SuperBDIRAC status & success rate\\
\mr
good-1 & 400 & INFN-T1 & 3 & 3 & 3 & 100\%\\
good-2 & 400 & INFN-T1 & 3 & 3 & 3 & 100\%\\
good-3 & 400 & INFN-T1 & 3 & 3 & 3 & 100\%\\
failure-1 & 10 & INFN-T1 & 2 & 2 & 2 & 100\%\\
failure-2 & 10 & INFN-T1 & 3 & 3 & 3 & 100\%\\
\br
\end{tabular}
\end{center}
\end{table}

BookKeeping database was properly updated for every job in every test. All status change were promptly displayed as well in SuperBDIRAC as in WebUI, without any appreciable delay between two portals. SQLAlchemy didn't introduced any appreciable delay or information loss, at least in this functionality test. 
Table \ref{tab:status_update} reports, for every test, how many status were saved in SBK and displayed in WebUI and SuperBDIRAC. Success rate was established as ratio between status saved in SBK and status displayed in SuperBDIRAC: its value was 100\% in all submissions.
SuperBDIRAC could be considered good enough to integrate in DIRAC the capability of monitoring jobs metadata from a bookkeeping database.

@@

- We are offering a Dirac extended suite capable to satisfy the
needs on small and mid size VOs in terms of distributed
resource exploitation....

@@

\bibitem{ref:superb_tdr}
Super$B$ Technical Design Report, \verb"http://arxiv.org/abs/1306.5655"
